*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-03 Code/Manuscript_O2.Rmd
Knitted

XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2 XXXXX 
In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration. The deep water environments typical for MIT 9313 are relatively nutrient rich and  *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004]. They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
Partensky *et al*. [@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, and c contributing to maintenance of the low O~2~ environment.

>>>>

XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2. Mirielle has notes, will add if relevant XXXXX 
In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration. The deep water environments typical for MIT 9313 are relatively nutrient rich and  *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004]. They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
Partensky *et al*. [@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, and c contributing to maintenance of the low O~2~ environment.
